Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers

### 2018-10-17 reports/paper.tex
get 80 character lines

\documentclass[%
 reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose,
%preprint,
%showpacs,preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 %aps,
 %prl,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-1}

@@

%
\begin{figure}[b]
\includegraphics[width=0.3\textwidth]{figures/head_groups}
\caption{\label{fig:heads}\small The two lipid classes with different head groups compared in this study, where R indicates the hydrocarbon tail; (a) phosphatidylglycerol (PG), (b) phosphocholine (PC).}
\end{figure}
%
We report on measurements of four phospholipids monolayers, namely 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG, C$_{14}$ tails), at the air-DES (1:2 choline choride:glycerol) interface.
In contrast to many previous studies\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990}, we have developed a chemically-consistent model (detail in the ESI) that allows for the co-refinement of reflectometry measurements at different surface pressure and makes no assumption of the volume of the lipid head, $V_h$, or tail, $V_t$.
Instead these parameters were allowed to vary for each lipid while being constrained to be self-consistent over different surface pressures in the same phase; Liquid-Condensed (LC) for DPPC and Liquid-Expanded (LE) for DMPC, DMPG and DLPC.
This model was required because we cannot assume that the electrostatic interactions between lipid head and the solvent are the same in the DES and in water. This may therefore influence the effective head volume which means we cannot rely on the literature values (see ESI) derived from measurements on or in water.
Furthermore, it is known that, on water, increased surface pressure and associated LE-LC phase transitions lead to a compression of the lipid tail volume\cite{Marsh2010,Small1984} and this compaction has not necessarily been accounted for in the literature\cite{Campbell2018}.
Our approach avoids this issue by making no assumption about the molecular volumes and only considering surface pressures that we believe to be in the same phase.

@@

The model, based on the standard two-layer model widely used for lipids on water, was first fitted to the experimental XRR data.
The associated SLD profiles are shown in Figure \ref{fig:lipids} while table \ref{tab:liptab} presents the results of the PDF for each of the varying parameters; the tail tilt angle, $\theta_t$, the interfacial roughness, $\sigma$, the head and tail volumes, $V_h$ and $V_t$ respectively, and the head layer thickness, $d_h$.
In order to constrain the fitting process only $\theta_t$ and $\sigma$ were allowed to vary independently of surface pressure. The other parameters, $V_h$, $V_t$ and $d_h$ were fitted to a single value for all of the surface pressures measured for each lipid.

@@

\end{document}
%
% ****** End of file apssamp.tex ******

>>>>

\documentclass[amsmath,amssymb,twocolumn]{revtex4-1}

@@

%
\begin{figure}[b]
\includegraphics[width=0.3\textwidth]{figures/head_groups}
\caption{\label{fig:heads}\small The two lipid classes with different head
groups compared in this study, where R indicates the hydrocarbon tail;
(a) phosphatidylglycerol (PG), (b) phosphocholine (PC).}
\end{figure}
%
We report on measurements of four phospholipids monolayers, namely
1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails),
1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails),
1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails) and
1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol)
(DMPG, C$_{14}$ tails), at the air-DES (1:2 choline choride:glycerol)
interface.
In contrast to many previous studies\cite{Mohwald1990,Kewalramani2010,
Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990}, we have developed
a chemically-consistent model (detail in the ESI) that allows for the
co-refinement of reflectometry measurements at different surface pressure
and makes no assumption of the volume of the lipid head, $V_h$, or tail, $V_t$.
Instead these parameters were allowed to vary for each lipid while being
constrained to be self-consistent over different surface pressures in the
same phase; Liquid-Condensed (LC) for DPPC and Liquid-Expanded (LE) for
DMPC, DMPG and DLPC.
This model was required because we cannot assume that the electrostatic
interactions between lipid head and the solvent are the same in the DES and
in water. This may therefore influence the effective head volume which means
we cannot rely on the literature values (see ESI) derived from measurements
on or in water.
Furthermore, it is known that, on water, increased surface pressure and
associated LE-LC phase transitions lead to a compression of the lipid tail
volume\cite{Marsh2010,Small1984} and this compaction has not necessarily
been accounted for in the literature\cite{Campbell2018}.
Our approach avoids this issue by making no assumption about the molecular
volumes and only considering surface pressures that we believe to be in the
same phase.

@@

The model, based on the standard two-layer model widely used for lipids on
water, was first fitted to the experimental XRR data.
The associated SLD profiles are shown in Figure \ref{fig:lipids} while
Table \ref{tab:liptab} presents the results of the PDF for each of the
varying parameters; the tail tilt angle, $\theta_t$, the interfacial
roughness, $\sigma$, the head and tail volumes, $V_h$ and $V_t$ respectively,
and the head layer thickness, $d_h$.
In order to constrain the fitting process only $\theta_t$ and $\sigma$ were
allowed to vary independently of surface pressure. The other parameters,
$V_h$, $V_t$ and $d_h$ were fitted to a single value for all of the surface
pressures measured for each lipid.

@@

\end{document}
